Homeostatic mechanisms may shape the type and duration of oscillatory modulation.

### 2020-05-04 main.tex
Fix - math typo

\section*{Methods}
\subsection*{Mathematical model}
We model an unconnected population of hippocampal neurons, subjected to oscillatory modulation. This is instantiated as $N = 1000$ input cells connected to $M = 100$ Hodgkin-Huxley neurons. The $M$ cells in the population were tuned to mimic regular firing \cite{Borgers2005,Borgers2008}. The firing pattern of each input cell (both stimulus and modulation) is from a Poisson process, with a time-varying rate. $N_o$ cells oscillate. $N_s$ serve as input. For simplicity, we let $N_o = \frac{N}{2}$ so $N_o = N_s$. All input cells have a $p = 0.1$ connection probability to the hippocampal population. The hippocampal population has no lateral of recurrent connections. The synaptic weights for all $N \rightarrow M$ connections $w$ were independently sampled from a uniform distribution, $w \sim \mathcal{U}(5, 50)$ $\mu$S. The firing rate of the oscillating population was governed by a biased sinusoidal pacemaker, with amplitude $\frac{r_o}$ and frequency $f$, with the exact form $\frac{r_o}{2} (1 + \text{sin}(2 \pi f t)) + r_b$. As a result, $r_o$ defines the peak firing of the oscillation. The stimulus population was simply modeled by a fixed rate of 6 Hz ($r_s$).

>>>>

\section*{Methods}
\subsection*{Mathematical model}
We model an unconnected population of hippocampal neurons, subjected to oscillatory modulation. This is instantiated as $N = 1000$ input cells connected to $M = 100$ Hodgkin-Huxley neurons. The $M$ cells in the population were tuned to mimic regular firing \cite{Borgers2005,Borgers2008}. The firing pattern of each input cell (both stimulus and modulation) is from a Poisson process, with a time-varying rate. $N_o$ cells oscillate. $N_s$ serve as input. For simplicity, we let $N_o = \frac{N}{2}$ so $N_o = N_s$. All input cells have a $p = 0.1$ connection probability to the hippocampal population. The hippocampal population has no lateral of recurrent connections. The synaptic weights for all $N \rightarrow M$ connections $w$ were independently sampled from a uniform distribution, $w \sim \mathcal{U}(5, 50)$ $\mu$S. The firing rate of the oscillating population was governed by a biased sinusoidal pacemaker, with amplitude $\frac{r_o}{2}$ and frequency $f$, with the exact form $\frac{r_o}{2} (1 + \text{sin}(2 \pi f t)) + r_b$. As a result, $r_o$ defines the peak firing of the oscillation. The stimulus population was simply modeled by a fixed rate of 6 Hz ($r_s$).
